Modal type theory based on the intuitionistic epistemic logic

### 2018-02-11 article.tex
added proof of coherence for tensorial strength in the term model

>>>>

$\begin{array}{lll}
&[p, {\bf let \: pure \:} x, y, z = ({\bf pure \:} \pi_1 p, {\bf let \: pure \:} p^{'} = \pi_2 p {\: \bf in \:} \pi_1 p^{'}, {\bf let \: pure \:} p^{'} = \pi_2 p {\: \bf in \:} \pi_2 p^{'}) & \\
&\quad\quad\quad\quad {\: \bf in \:} \langle x, \langle y, z \rangle\rangle] = & \\
&[p, {\bf let \: pure \:} x, p^{'}, z = ({\bf pure \:} \pi_1 p, \pi_2 p, {\bf let \: pure \:} p^{'} = \pi_2 p {\: \bf in \:} \pi_2 p^{'}) {\: \bf in \:} \langle x, \langle \pi_1 p^{'}, z \rangle\rangle] = & \\
&[p, {\bf let \: pure \:} x, p^{'} = {\bf pure \:} \pi_1 p, \pi_2 p {\: \bf in \:} \langle x, \langle \pi_1 p^{'}, \pi_2 p^{'} \rangle\rangle]&
\end{array}$

$\begin{array}{lll}
&\tau_{\hat{A}, \hat{B} \times \hat{C}} \circ (id_{\hat{A}} \times \tau_{\hat{B}, \hat{C}}) \circ \alpha_{\hat{A}, \hat{B}, {\bf K}\hat{C}} = & \\
&\tau_{\hat{A}, \hat{B} \times \hat{C}} \circ [q, \langle \pi_1 q, {\bf let \: pure \:} y, z = {\bf pure \:} (\pi_1 (\pi_2 q)), \pi_2 (\pi_2 q) {\: \bf in \:} \langle y, z \rangle \rangle] \: \circ & \\
&\quad\quad\quad\quad \circ \: [p, \langle \pi_1 (\pi_1 p), \langle \pi_2 (\pi_1 p), \pi_2 p \rangle \rangle] = & \\
&\tau_{\hat{A}, \hat{B} \times \hat{C}} \circ [p, \langle \pi_1 q, {\bf let \: pure \:} y, z = {\bf pure \:} (\pi_1 (\pi_2 q)), \pi_2 (\pi_2 q) {\: \bf in \:} \langle y, z \rangle \rangle & \\
&\quad\quad\quad\quad [q := \langle \pi_1 (\pi_1 p), \langle \pi_2 (\pi_1 p), \pi_2 p \rangle \rangle]] = & \\
&\tau_{\hat{A}, \hat{B} \times \hat{C}} \circ [p, \langle \pi_1 (\pi_1 p), {\bf let \: pure \:} y, z = {\bf pure \:} \pi_2 (\pi_1 p), \pi_2 p {\: \bf in \:} \langle y, z \rangle \rangle] = & \\
&[r, {\bf let \: pure \:} x, p^{'} = {\bf pure \:} \pi_1 r, \pi_2 r {\: \bf in \:} \langle x, \langle \pi_1 p^{'}, \pi_2 p^{'} \rangle\rangle] \: \circ & \\
&\quad\quad\quad\quad \circ \: [p, \langle \pi_1 (\pi_1 p), {\bf let \: pure \:} y, z = {\bf pure \:} \pi_2 (\pi_1 p), \pi_2 p {\: \bf in \:} \langle y, z \rangle \rangle] = & \\
&[p, {\bf let \: pure \:} x, p^{'} = ({\bf pure \:} (\pi_1 (\pi_1 p)), {\bf let \: pure \:} y, z = ({\bf pure \:} \pi_2 (\pi_1 p), \pi_2 p {\: \bf in \:} \langle y, z \rangle \rangle) & \\
&\quad\quad\quad\quad {\: \bf in \:} \langle x, \langle \pi_1 p^{'}, \pi_2 p^{'} \rangle\rangle ] = & \\
&[p, {\bf let \: pure \:} x,y,z = {\bf pure \:} (\pi_1 (\pi_1 p)), {\bf pure \:} \pi_2 (\pi_1 p), \pi_2 p {\: \bf in \:} \langle x, \langle \pi_1 p^{'}, \pi_2 p^{'} \rangle\rangle [p^{'} := \langle y, z \rangle]] = & \\
&[p, {\bf let \: pure \:} x,y,z = {\bf pure \:} (\pi_1 (\pi_1 p)), {\bf pure \:} \pi_2 (\pi_1 p), \pi_2 p {\: \bf in \:} \langle x, \langle y, z \rangle\rangle]&
\end{array}$
